---
title: "FSB Internship Dashboard 2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )
#read in data
final_df <- read.csv('final_df.csv')
```

# Question and Insights {data-orientation=columns}

### Question

Using the FSB Student Survey, we are looking to answer these three questions:

1. If you have at least one internship, how much more likely are you to have a full-time job than if you did not have an internship?

2. What if you have two internships?

3. Does having an internship mean your salary level will be higher in your full-time job?

### Insights



# Survey Overview {data-orientation=columns}

Overview of survey responses
  
## row {data-width=300}

### Response Rate

```{r, echo = FALSE}
rate = round(100*nrow(final_df)/(1250*3), 0)
gauge(rate, min=0, max=100, symbol='%', gaugeSectors(
  success = c(70,100), warning = c(40,69), danger = c(0,39)
))
```

### Usable Responses

```{r,echo=FALSE}

```   
 

## row {data-height=600}

### Internship Breakdown

This graph will be the number of internships on the x axis with the number of responses on the y axis.

```{r,echo=FALSE}

```


### Post-Graduation Plans

Survey plans on the x-axis to the number of responses on the y axis. 
    
```{r,echo=FALSE}

```
   
   

# Internships to Full-Time Jobs {data-orientation=columns}

## Column {data-width=400}

### Percentage of Full-Time Placement between 1 and 2 Internships

This graph is going to look at the full-time job placement difference between students that had one internship vs. students that had two internships (question 3b).

```{r,echo=FALSE}

```

### Internship to Salary Impact

We will do mean imputation for the N/A salary values by major to fill in the data that is missing. This graph will answer question 3c to see if there is a difference in salary if a student has an internship or not. 

```{r,echo=FALSE}

```


## Column {data-width=600}

### Number of Internships to Full-Time

This graph will look similar to 'Internship Status by Career Fair Attendance' on the in-class example. We will have internship number on the x axis, response amount on the y axis, and color it by fulltime job or no fulltime job (question 3a). 

```{r,echo=FALSE}

```

