---
title: "FSB Internship Dashboard 2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package initialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT, #for better tables
               scales # for formatting axis labels
               )
#read in data
final_df <- read.csv('final_df.csv')
```

# Project Overview {data-orientation="columns"}

## row {data-width="700"}

### Project Statement

For this project, we wanted to better understand the importance of internships in college. Specifically, we used the FSB Student Survey from 2019-2021 to answer the following questions:

1.  If you have at least one internship, how much more likely are you to have a full-time job than if you did not have an internship?

2.  What if you have two internships?

3.  Does having an internship mean your salary level will be higher in your full-time job?

Before diving into the data, we created a business value proposition (see below) to better understand our customer's pain points and the potential gain creators we can make. 

### Business Value Proposition

![](images/poster Value proposition canvas simple white (2).png)

## row {data-height="600"}

### Insights

After analyzing our data, we found answers to each of the three questions above:

1.  Looking at the tab titled "Internships to Full-Time Jobs", the graph of "Percentage of Students with Full-Time Jobs by Number of Internships" shows that 57.69% of students who had 0 internships got full-time jobs post graduation, while 83.04% of students who had 1 internship got a full-time job. We can also see that students with 2, 3, 4, and 5 internships all had full-time job percentages much higher than students with 0 internships.

2.  Looking at the tab titled "Internships to Full-Time Jobs", the graph of "Percentage of Students with Full-Time Jobs by Number of Internships" shows that 83.04% of people who had 1 internship got a full-time job post graduation, while 89.31% of students with 2 internships got a full-time job post graduation.

3.  Looking at the tab titled "Internships to Full-Time Jobs", the graph of "Average Salaries by Internships" shows that there is a \~\$5,000 difference in starting salary between students who had one internship vs. students who had zero internships.

# Description of Deliverables {data-orientation="rows"}

## row {data-width="500"}

### Survey Overview Section
In this tab of our analysis, we have included 4 different visualizations that we believe are important for our client. This section is intended to serve as an overview of the data and to give our client a brief, but easily understandable view of the student's responses. Below, we have explained each of the 4 visualizations in-depth:

1. **Response Rate**: This is a graphic that shows the percentage of graduating students from 2019-2021 that responded to the FSB Internship & Full-Time Placement survey. It is important to see this percentage in order for the client to understand what percentage of students responded to the survey and that there might be missing  responses. 

2. **Usable Responses**: This is the number of responses we had available to use in our analysis. It is important for the client to get this background before diving into the graphics so they have a better understanding of how many students' answers were taken into account in this analysis. 

3. **Internship Breakdown**: This is a bar chart that shows the amount of students compared with the number of internships they had during their college career. This is a great breakdown to show the client so they better understand any skew in the amount of internships had by students in FSB. They can also see how many students had no internships vs. 1+ internships in FSB during their college career. 

4. **Post-Graduation Plans**: This is a bar chart that shows different post-graduation plans the number of students pursing each option. It is important for our client to get an overview of what FSB students are doing after graduation as this could help them understand what paths FSB students may be interested in in the future.

### Internships to Full-Time Jobs Section

The Internships to Full-Time section of our analysis contains deliverables that directly answer our original project questions. Below, we have developed descriptions of each deliverable:

1. **Number of Internships to Full-Time**: This is an interactive bar chart that shows the number of internships (0-5) on the x-axis and number of responses on the y-axis with the fill of the graph being full-time job placement ("yes" or "no"). There are a lot of insights to be derived from this graph. This graph is important to show a visual representation of the amount of students who landed full-time jobs vs. those who did not in each internship amount category. 

2. **Average Salaries by Internships**: This is a bar chart that shows the average full-time job salary of students who had 0 internships in college and students who had at least 1 internship in college. This is important for the client when trying to answer question #3 on the "Project Overview" tab asking if a student's salary will be higher if they had internships in college vs. if they did not.

3. **Percentage of Students with Full-Time Jobs by Number of Internships**: This is a bar chart that shows the percentage of students who landed full-time jobs in each internship amount category. This graph directly answers questions 1 and 2 from the "Project Overview" tab asking about the likelihood of a student landing a full-time job if they had internships in college vs. not having an internship. 

# Survey Overview {data-orientation="columns"}

Overview of survey responses

## row {data-width="500"}

### Response Rate

```{r, echo = FALSE}
rate <- round(100 * nrow(final_df) / (1250 * 3), 0)

gauge(rate,
  min = 0,
  max = 100,
  symbol = '%',
  gaugeSectors(
    success = c(70, 100),
    warning = c(40, 69),
    danger = c(0, 39)
  )
)

```

### Usable Responses

```{r,echo=FALSE}
nusable <- nrow(final_df)
valueBox(nusable, icon = "fa-users")
```

### Internship Breakdown

```{r,echo=FALSE}
p <- ggplot(final_df, aes(x = survey_internships)) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  xlab("Number of Internships") +
  ylab("Number of Responses") +
  theme_bw()

ggplotly(p)
```

## row {data-height="600"}

### Post-Graduation Plans

```{r,echo=FALSE}
p <- final_df %>%
  ggplot(aes(x = reorder(survey_plans, survey_plans, function(x) -length(x)))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  xlab("Post Graduation Plans") +
  ylab("Number of Responses") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45))

ggplotly(p)
```

# Internships to Full-Time Jobs {data-orientation="columns"}

## Column {data-width="400"}

### Number of Internships to Full-Time

```{r,echo=FALSE}
final_df$fulltimejob_yes <- ifelse(final_df$fulltimejob == 1, "yes", "no")
final_df$fulltimejob_yes <- as.factor(final_df$fulltimejob_yes)

p <- final_df %>%
  ggplot(aes(x = survey_internships, fill = fulltimejob_yes)) +
  geom_bar(color = "steelblue") +
  xlab("Amount of Internships") +
  ylab("Number of Responses") +
  theme_bw() +
  labs(fill = "Full-Time Job")

ggplotly(p)

```

### Average Salaries by Internships

```{r,echo=FALSE}
final_df <- final_df %>%
  mutate(internship = ifelse(survey_internships == 0, "no", "yes"))

final_df_mean_salaries <- final_df %>%
  filter(fulltimejob != 0) %>%
  group_by(major1) %>%
  mutate(survey_salary = ifelse(is.na(survey_salary), mean(survey_salary, na.rm = TRUE), survey_salary))

mean_salary_data <- final_df_mean_salaries %>%
  group_by(internship) %>%
  summarise(mean_salary = round(mean(survey_salary, na.rm = TRUE)),0)

p <- ggplot(mean_salary_data, aes(x = internship, y = mean_salary)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  xlab("Internships (Yes/No)") +
  ylab("Mean Survey Salary") +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  geom_text(aes(label = mean_salary), vjust = -0.5) + 
  theme_bw()

ggplotly(p)

```

## Column {data-width="600"}

### Percentage of Students with Full-Time Jobs by Number of Internships

```{r,echo=FALSE}
# Add a new column 'fulltimejob_yes' based on the 'fulltimejob' column
final_df$fulltimejob_yes <- ifelse(final_df$fulltimejob == 1, "yes", "no")
final_df$fulltimejob_yes <- as.factor(final_df$fulltimejob_yes)

# Calculate the percentage of 'yes' responses and the count based on 'survey_internships'
percentage_data <- final_df %>%
  group_by(survey_internships) %>%
  summarize(
    percentage = sum(fulltimejob_yes == "yes") / n(),
    count = n()
  )

# Create a bar plot of the calculated percentages
p <- percentage_data %>%
  ggplot(aes(x = survey_internships, y = percentage)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  xlab("Amount of Internships") +
  ylab("Percentage of 'yes' responses") +
  theme_bw() +
  labs(fill = "Full-Time Job") +
  geom_text(aes(label = scales::percent(percentage)), vjust = -0.5)

# Convert the plot to an interactive plot using ggplotly
ggplotly(p)

```
