---
title: "Student Success"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Madison Jones and Brady Losiewicz"
format: 
  html:
    toc: true
    toc-location: left
    toc-expand: true
    code-tools: true 
    code-fold: true
    code-overflow: scroll
    self-contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Test Change
Dr. Farmer is testing a change in this file to see if we can run the document without changing the working directory.

I'm adding another change


## Inserting Data

```{r}
df <- readRDS('FSB_BI_Survey_2019_2021.rds')
head(df)
```


## Creating a Clean Subset

### Cleaning the Full-Time Placements

**Omitting colummns that are not helpful to data insights charge number #3 (internships to full time placements)**
```{r}
new_df <- subset(df, select = c(32:38))
new_df$survey_salary = df$survey_salary
head(new_df)
str(new_df)
```

**Turning survey_plans column into a factored column**
```{r}
new_df$survey_plans = as.factor(new_df$survey_plans)
```

**Omitting all null values for survey_plans:**
```{r}
new_df <- new_df[!is.na(new_df$survey_plans), ]
head(new_df)
str(new_df$survey_plans)
```

**Making a column that has a "1" if the candidate has accepted a fulltime job OR they have at least 1 offer, otherwise "0":**
```{r}
new_df$fulltimejob <- ifelse((new_df$survey_offers >= 1 & !is.na(new_df$survey_offers) ) | new_df$survey_plans == "accepted fulltime job", 1, 0)
head(new_df, 10)
```

**Rationale for the "fulltimejob" column:**

We wanted to count full-time job placement as anyone who has done one of the following:
* said that they "accepted a fulltime job" as their survey plan
* put that they got at least 1 offer in their survey

We decided to add the second criteria bullet to full-time job placements because even if someone is, for example, "continuing their education" in the future, if they got at least 1 offer, they could have had a full time job. Since we are solely looking at full-time job placements, we wanted to look at everyone who has a full-time job or could've chosen to take a full-time job if they had at least one offer. 


### Cleaning the Internship Placements

We want to easily see how many internships each candidate has. 

Making four different columns that show "1" if the candidate has one, two, three, or four internships:
```{r}
new_df$internships_one <- ifelse(!is.na(new_df$survey_internone), 1, 0)
new_df$internships_two <- ifelse(!is.na(new_df$survey_interntwo), 1, 0)
new_df$internships_three <- ifelse(!is.na(new_df$survey_internthree), 1, 0)
new_df$internships_four <- ifelse(!is.na(new_df$survey_internfour), 1, 0)
head(new_df)
```

Adding another column that sums the amount of internships:
```{r}

```


